New lower bounds for Schur and weak Schur numbers

### 2022-02-24 article/soumission_SIAM/weakschur.tex

\par
Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
corresponding to the third inequality can be found in the \ref{WS-templates}.

@@

However, trying out all of the 2\,447\,113\,088 Schur number 5-partitions \cite{Heule2017} one by one would not result in a 
reasonable computation time: it is necessary to test the construction on several partitions at once. We encoded the problem as a 
satisfiability problem and used the 1616 backdoors that were used in \cite{Heule2017} in order to encode a group of partitions in 
a compact and efficient way. Among all of the 1616 backdoors, only the 911\textsuperscript{th} backdoor gave a weakly sum-free 
partition of length 643. This backdoor gave a weakly sum-free partition of length 646 and cannot give a weakly sum-free 
partition of length 647. A weakly sum-free partition of length 646 can be found in the \ref{WS(6)}.

>>>>

\par
Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
corresponding to the third inequality can be found in \ref{WS-templates}.

@@

However, trying out all of the 2\,447\,113\,088 Schur number 5-partitions \cite{Heule2017} one by one would not result in a 
reasonable computation time: it is necessary to test the construction on several partitions at once. We encoded the problem as a 
satisfiability problem and used the 1616 backdoors that were used in \cite{Heule2017} in order to encode a group of partitions in 
a compact and efficient way. Among all of the 1616 backdoors, only the 911\textsuperscript{th} backdoor gave a weakly sum-free 
partition of length 643. This backdoor gave a weakly sum-free partition of length 646 and cannot give a weakly sum-free 
partition of length 647. A weakly sum-free partition of length 646 can be found in \ref{WS(6)}.
